%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.1 (February 24, 2025)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

\newcommand{\tightentrywithorg}[2]{%
  \noindent
  \begin{tabular}{@{}p{1.6cm}p{0.7\linewidth}@{}} % Adjust 2.5cm width as needed
    \textbf{#1} & #2
  \end{tabular}
  \vspace{0.3em} % Space between entries
}

\newcommand{\tightentry}[1]{%
  \par\noindent{#1}\par\vspace{0.2em}
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % Left column with your name and title, change the width as needed
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short: use just one of the lines below
	% If your name is very long: reduce the font size or make the current column wider (and reduce the others proportionately)
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Jack}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Edge}}}}} % Last name
	
	\vspace{6pt} % Vertical whitespace
	
	{\huge Research Paramedic} % Career or current job title
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.27\textwidth} % Center column with the first column of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome5.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{London/Berlin}\\
	\icon{Phone}{12}{+44 7878 584 035}\\
	\icon{At}{12}{\href{mailto:hello@jmge.io}{hello@jmge.io}}\\	
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.27\textwidth} % Right column with the first column of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome5.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://img.jmge.io}{img.jmge.io}}\\
	\icon{Github}{12}{\href{https://github.com/jackgedge}{github.com/jackgedge}}\\
	\icon{Twitter}{12}{\href{https://x.com/jackgedge}{@jackgedge}}\\
\end{minipage}

\vspace{0.3cm} % Vertical whitespace

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.6\textwidth} % Left column with the introduction text, change the width as needed
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Who Am I?}
	\vspace{-0.5em}

	Data enthusiast. In the final year of my MSc completing a systematic review in Python and LaTeX. Back after two years on a remote coral atoll, building data pipelines and teaching IT literacy on a refugee project. Keen to deepen my statistical-modelling skills, gain experience in UK research and — true to my paramedic roots — help turn data into evidence-based improvements in pre-hospital care.
	\\ % Dummy text
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.38\textwidth} % Right column with the skills bar chart, change the width as needed
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\begin{barchart}{5.5} % The parameter to the barchart environment is the maximum width (in cm) of the longest bar
		\baritem{Resuscitation}{80}
		\baritem{Python}{70}
		\baritem{Excel}{60}
		\baritem{Cycling}{70}
		\baritem{Photography}{65}
		\baritem{LaTeX}{30}
	\end{barchart}
\end{minipage}

% Output a series of bubbles showing your proficiency with environments and/or tools
% \begin{center}
%	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender} % Each bubble must be in the format of '<size>/<label>' and you can specify as many bubbles as will fit on the page
% \end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.61\textwidth}
	\vspace{-\baselineskip}
	
	\cvsect{Experience}

	\begin{entrylist}
		\entry
			{3/2023 11/2024}
			{Advanced Life Support Paramedic}
			{Response-Med, Diego Garcia, BIOT}
			{For two years I provided 24/7 critical and primary care to a remote community of Tamil refugees, working in a multidisciplinary team while handling highly sensitive records in real time. Seeing that no data were being captured, I designed and ran a Microsoft 365 patient-record system and an Excel disease-surveillance database—robust enough for austere conditions yet simple for non-technical colleagues. Each week I extracted, cleaned and analysed clinical and operational data in Python, R and Excel, producing concise reports that guided local decisions and informed international partners; a UNHCR briefing drawn from this work was later cited by the BBC. I set up rapid-reporting workflows for ad-hoc requests, helped write SOPs, and introduced a 24-hour rota to protect documentation quality and service continuity. Day-to-day duties included strict infection-control, equipment checks, and inventory management to keep the clinic mission-ready, all while delivering culturally sensitive care and mental-health first aid to a population shaped by trauma.\\ \texttt{Python}\slashsep\texttt{Microsoft 365}\slashsep\texttt{Remote Medicine}}
		\entry
			{5/2021 Now\\\footnotesize{part time}}
			{Emergency Care Paramedic}
			{Kingston ED Resus, London, UK}
			{Lead role in a busy resuscitation area, bridging the gap between ambulance crews and critical care teams. Translating pre-hospital handovers into clear in-hospital care plans. Immersed in a new clinical environment—with complex patients, unfamiliar equipment and strict documentation standards—I actively seek feedback, learn rapidly and share what I learn with colleagues. I stay calm under pressure while co-ordinating multidisciplinary responses, double-checking drug calculations and device settings, and ensuring every detail is logged accurately in NHS electronic records.\\ 
			\texttt{Collaboration}\slashsep\texttt{Detail}\slashsep\texttt{Emergency Department}}
		\entry
			{3/2016 \\2/2024\\\footnotesize{part time}}
			{Paramedic}
			{London Ambulance Service, pan-London, UK}
			{Responded across London—solo and with a crewmate—to critical medical and trauma calls, delivering first-on-scene interventions and safe transfers. The work sharpened calm, patient-first communication in every setting and required ePCRs completed to audit standard before shift close. I mentored new clinicians in advanced triage, rapid decision-making and evidence-based care—embodying EAAA’s “Together we save lives” spirit. One incident (bus-vs-pedestrian on Oxford Street) earned me an Excellence Report, praising my scene leadership, assertive yet respectful communication, and creation of a calm working environment under intense public scrutiny.\\ \texttt{Resuscitation}\slashsep\texttt{Mentorship}\slashsep\texttt{Pre-Hospital Care}}
			
	\end{entrylist}
	\end{minipage}
	\hfill % Automatic horizontal whitespace
	\begin{minipage}[t]{0.365\textwidth} % Right column width
		\vspace{-\baselineskip} % Required for vertically aligning minipages

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

		\cvsect{Education}

		\begin{entrylist}
			\entry
				{2024 \\Now}
				{Master's Degree\\Emergency \& Resuscitation Medicine}
				{\\Queen Mary, University of London}
				{\textit{“Does motivation matter? A systematic review and meta-analysis of outcomes following intentional foreign object ingestion”}. For a peer-reviewed journal.}
			\entry
				{2020\\2022}
				{Graduate Diploma\\Emergency \& Resuscitation Medicine}
				{\\Queen Mary, University of london}
				{Distinction}
			\entry
				{2007\\2013}
				{Foundation Degree\\Paramedic Science}
				{\\St George's, University of London}
				{Merit}
		\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL QUALIFICATIONS
%----------------------------------------------------------------------------------------

	\vspace{-1.5em}
		\cvsect{Data}
			\vspace{-0.5em} % remove whitespace below title

			\tightentrywithorg{Microsoft}{Azure Fundamentals (AZ-900)}
			\tightentrywithorg{Google}{IT Support Professional Certification}
			\tightentrywithorg{IBM}{Introduction to Data Engineering}
			\tightentrywithorg{}{Python for Data Science, AI \& Development}
			\tightentrywithorg{Harvard}{CS50x Introduction to Computer Science (ongoing)}

			\vspace{-1.3em}
		\cvsect{Clinical}
			\vspace{-0.5em}

			\tightentrywithorg{AHA}{PALS Provider}
			\tightentrywithorg{}{ACLS Provider}
			\tightentrywithorg{UKRC}{ALS}
			\tightentrywithorg{OPITO}{BOSIET}

			\vspace{-1.3em}
		\cvsect{Memberships}
			\vspace{-0.5em}
			
			\tightentrywithorg{HCPC}{UK Registered Paramedic (PA40515)}
			\tightentrywithorg{DVLA}{A, B, C1 Licences}
			\tightentrywithorg{IAM}{Institute of Advanced Motorists (51320581)}
			\tightentrywithorg{MCPara}{Member College of Paramedics (CP008451)}

	\end{minipage}
%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.2\textwidth} % Left column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	\vspace{-0.5em}

	\textbf{English} - native\\
	\textbf{German} - proficient\\
	\textbf{Spanish} - rudimentary
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.3\textwidth} % Center column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	\vspace{-0.5em}

	I love wildlife and portrait - capturing biology in motion. Bicycles, cycling, computers, tech, lifting weight and meditation too.
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.365\textwidth} % Right column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	\vspace{-0.5em}
	
	I’ve volunteered in Calais’ “Jungle” refugee camp, completed charity bike rides and a high-rise zip-line, and travelled to Malawi to help build a remote school.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
